D3064R0: Is OOTA Execution Vacuous for Real-World C++ Implementations?

### 2024-01-09 ootavacuous.tex
Apply Alan Stern feedback on abstract and conclusion
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

	This paper refactors the commonly used condition for detecting
	OOTA behavior, which permits bringing to bear constraints from
	long-standing laws of physics and on hardware systems.
	These constraints prevent OOTA cycles containing only volatile
	atomics from occurring in correctly constructed C++ programs
	running on correctly constructed C++ implementations in our
	current universe.
	Given current optimizations, these constraints also prevent
	OOTA cycles involving non-volatile atomics.

	In this, OOTA behaviors are similar to the issues surrounding
	undecidability and its real-world counterpart, high complexity.
	So similar, in fact, that not only the same strategies apply
	to OOTA, but also the same \emph{code} applies, both for C++
	implementations and for associated tooling.
\end{abstract}

@@

This paper has refined the definition of ``OOTA cycle'' from
\co{acyclic(sdep; rf)} to \co{acyclic(sdep; rfe)}, which enables the
application of temporal reasoning to OOTA analysis of the C++ memory
model.
This reasoning shows that correct real-world C++ implementations relying
on single-threaded analyses are inherently incapable of producing OOTA
cycles from UB-free programs using volatile atomics.

C++ implementations that additionally refrain from inventing atomic loads
and that also ensure that each atomic load that is executed corresponds
to a specific load in the abstract machine are incapable of producing
OOTA cycles from UB-free programs using non-volatile as well as volatile
atomics.

>>>>

	This paper refactors the commonly used condition for detecting
	OOTA behavior, which permits bringing to bear constraints from
	long-standing laws of physics and on hardware systems.
	These constraints prevent OOTA cycles containing only volatile
	atomics from occurring in UB-free executions of C++ programs
	running on correctly constructed C++ single-thread analysis
	implementations in our current universe.
	Given current optimizations, these constraints also prevent
	OOTA cycles involving non-volatile atomics.
\end{abstract}

@@

This paper has refined the definition of ``OOTA cycle'' from
\co{acyclic(sdep; rf)} to \co{acyclic(sdep; rfe)}, which enables the
application of temporal reasoning to OOTA analysis of the C++ memory
model.
This reasoning shows that correct real-world C++ implementations relying
on single-threaded analyses are inherently incapable of producing OOTA
cycles in UB-free executions of programs using volatile atomics.

C++ implementations that additionally refrain from inventing atomic loads
and that also ensure that each atomic load that is executed corresponds
to a specific load in the abstract machine are incapable of producing
OOTA cycles in UB-free executions of programs using non-volatile as well
as volatile atomics.
